Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-01-10 paper/PCSC2019-sigconf.tex
New results

\documentclass[sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs} % For formal tables

@@

% The default list of authors is too long for headers.
\renewcommand{\shorttitle}{Implementation and Analysis}
% \renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings.\footnote{This is an abstract footnote}
\end{abstract}

@@

\keywords{ACM proceedings, \LaTeX, text tagging}

@@

\begin{acks}
  The authors would like to thank Dr. Yuhua Li for providing the
  MATLAB code of the \textit{BEPS} method.

>>>>

\documentclass[sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xinttools}
\usepackage{array}
\usepackage{booktabs} % For formal tables

@@

% The default list of authors is too long for headers.
\renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
% \renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy, In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dasgupta--Pal, and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations. Preliminary results have shown that the Pailler and Dasgupta--Pal cryptosystems are comparable in accuracy and may be used to approximate a logarithm transformation, but the Dasgupta--Pal cryptosystem is significantly slower.
\end{abstract}

@@

\keywords{homomorphic encryption, image operations, facial recognition, numerical approximations}

@@

\begin{acks}
  The authors would like to thank Dr. Yuhua Li for providing the
  MATLAB code of the \textit{BEPS} method. Testing testing.

### 2019-01-10 paper/appendix.tex
New results

\section{Correction for Dasgupta--Pal}
\label{chap:correction}
\subsection{Bitwise Description of the Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \textsc{ xor } b = (a + b) \bmod 2
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \textsc{ and } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\subsection{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

@@

			Therefore, the parity of $a+b$ is the same as the parity of $r$.
		\item[Case 2: $ab$ is even.]
			Since $ab = S_kq + r$, $S_kq + r$ must also be even.
			$S_k$ is even, so $S_kq$ is also even. For $S_kq + r$ to be even, $r$ must be even , since $S_k$ is even.

@@

Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the exponential or logarithmic function.

@@

%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
%TODO: Include citations for this chapter
\subsection{Approximation for $\log(1+x)$}
\label{sec:logapproximation}
We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
\cite{khattri_new_2009}.
We let $x = 1/n$ and consider the integral
\begin{align*}
  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
\end{align*}

This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}, which is as follows:
\begin{align*}
	\int_a^b{f(x)\diff x}
	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}\\
	\int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)}
\end{align*}
where
\begin{multicols}{2}
	\noindent
	\begin{align*}
		w_1 &= 0\\
		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}\\
	\end{align*}
	\columnbreak
	\begin{align*}
		x_1 &= \frac{128}{225}\\
		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
	\end{align*}
\end{multicols}
This yields the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) \approx
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}
While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
    \label{fig:standardquadrature}
\end{figure}
As we only need accuracy for $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
\begin{align*}
  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
  &= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
  &= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}
\end{align*}

Using the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$, we arrive at the approximation:
\begin{align}\label{eq:scaledquadrature}
  \begin{split}
    &\log(1+x) \\
    &\approx \frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} \\
    &+ \log{20}
  \end{split}
\end{align}
Below is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
\begin{figure}[h]
    \centering
    \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
    \label{fig:scaledquadrature}
\end{figure}

\subsection{Approximation for $x^\gamma$}
To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
\end{align*}
This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.

>>>>

\section{Correction for Dasgupta--Pal}
\label{chap:correction}
\subsection{Bitwise Description of the Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[\textsc{xor} on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \textsc{ xor } b = (a + b) \bmod 2
	\end{align*}
	\item[\textsc{and} on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \textsc{ and } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\subsection{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

@@

			Therefore, the parity of $a+b$ is the same as the parity of $r$.
		\item[Case 2: $ab$ is even.]
			Since $ab = S_kq + r$, $S_kq + r$ must also be even.
			$S_k$ is even, so $S_kq$ is also even. For $S_kq + r$ to be even, $r$ must be even, since $S_k$ is even.

@@

Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the transcendental function.

@@

\subsection{Approximation for $\log(1+x)$}
\label{sec:logapproximation}
We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
\cite{khattri_new_2009}.
We let $x = 1/n$ and consider the integral
\begin{equation}
	\label{eq:log_integral}
  	\int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
\end{equation}

This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}. We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
\begin{align*}
	\int_a^b{f(x)\diff x}
	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
\end{align*}
Then, we approximate the integral using the following summation:
\begin{align*}
  \int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
\end{align*}
where
\begin{multicols}{2}
	\noindent
	\begin{align*}
		w_1 &= 0\\
		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}
	\end{align*}
	\columnbreak
	\begin{align*}
		x_1 &= \frac{128}{225}\\
		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)
	\end{align*}
\end{multicols}
Applying this procedure to the integral in equation \ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) \approx
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}

While the closed form approximation in equation \ref{eq:standardquadrature} is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in figure \ref{fig:standardquadrature}.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
    \label{fig:standardquadrature}
\end{figure}

As we only need accuracy for arguments $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
\begin{align*}
  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
  &= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
  &= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}
\end{align*}

Applying the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$ using SageMath 8.3, we arrive at the approximation:
\begin{align}\label{eq:scaledquadrature}
  \begin{split}
    &\log(1+x) \\
    &\approx \frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} \\
    &+ \log{20}
  \end{split}
\end{align}

Figure \ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$. Using SageMath 8.3, it was numerically determined that the maximum absolute error of this approximation in the range $x\in[0,255]$ is approximately $0.0103315865985758$, occurring at $x=255$. This is an improvement from the approximation in equation \ref{eq:standardquadrature}, which has a maximum absolute error of $1.19717868468392$, similarly occurring at $x=255$.

\begin{figure}[h]
    \centering
    \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
    \label{fig:scaledquadrature}
\end{figure}

\subsection{Approximation for $x^\gamma$}
To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
\end{align*}

This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}

As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.
